Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 qcd.tex
clearer confinement description

    Another consequence of the running coupling
    is colour confinement, in which quarks and
    gluons cannot exist as free particles. Due
    to the increasing strength of coupling at low
    energies, quarks and gluons are forced to
    form composite, colourless particles. This means
    that at low energies, perturbative QCD
    is not an accurate description of nature,
    and the behaviour of hadrons cannot be predicted
    from perturbation theory. Instead phenomenological
    models have to be used to describe these processes.
    This will be briefly touched on in Section~\ref{sec:anatomy_event}.

>>>>

    At low energies, quarks and gluons cannot exist as free
    particles and are forced to form composite, colourless
    particles. This phenomenon, named confinement, is compatible
    with the observation of the running coupling, but the
    perturbative calculation predicting the running coupling
    does not necessarily lead to the non-perturbative phenomenon
    of confinement.
    This means that at low energies, perturbative QCD
    is not an accurate description of nature,
    and the behaviour of hadrons cannot be predicted
    from perturbation theory. Instead phenomenological
    models have to be used to describe these processes.
    This will be briefly touched on in Section~\ref{sec:anatomy_event}.
